### 2013-09-26 evaluation/paper.tex
remove typos, thank vlad some more :)

\subsection{Experiments using Exact Inference}
In this section, we present results on multi-class classification, sequence
labeling and multi-label prediction. In these tasks, exact inference is
possible, and we can compute the exact objective of the various algorithms
easily. We use the dynamic programming algorithm implemented in \textsc{OpenGM}
for experiments for the tree and chain models.
For the full pairwise multi-label model, we use branch-and-bound together with
the AD$^3$ algorithm. %FIXME AD3 solver description?
We found that using the linear programming relaxation on the \textsc{scene} dataset is
often tight, and there was no need to resort to approximate inference. Inference
on the \textsc{yeast} dataset was more complex, and on the verge of being non-practical.
We use this dataset as an example for very costly inference.

@@

\subsection{Experiments using Approximate Inference}
For the remaining tasks, the \textsc{snakes} dataset and image segmentation, exact
inference is intractable for learning.
%
We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and the linear programming relaxation provided by AD$^3$
not using branch-and-bound, in contrast to the multi-label setup above.

>>>>

\subsection{Experiments using Exact Inference}
In this section, we present results on multi-class classification, sequence
labeling and multi-label prediction. In these tasks, exact inference is
possible, and we can compute the exact objective of the various algorithms
easily. We use the dynamic programming algorithm implemented in \textsc{OpenGM}
for experiments using the tree and chain models.
For the full pairwise multi-label model, we use branch-and-bound together with
the AD$^3$ algorithm.
We found that using the linear programming relaxation on the \textsc{scene} dataset is
often tight, and there was no need to resort to approximate inference. Inference
on the \textsc{yeast} dataset was more complex, and on the verge of being non-practical.
We use this dataset as an example for very costly inference.

@@

\subsection{Experiments using Approximate Inference}
For the remaining tasks, the \textsc{snakes} dataset and image segmentation, exact
inference is intractable for learning.
%
We use two different approximate inference algorithms, fusion
moves~\citep{lempitsky2010fusion}, a fast local search procedure, and the
linear programming relaxation provided by AD$^3$~\citep{martins2011augmented}
not using branch-and-bound, in contrast to the multi-label setup above.

### 2013-09-26 main.tex
more fixes via vlad :)
remove typos, thank vlad some more :)

During my work on this dissertation, my ideas were shaped by many of my fellow
students and researchers. First and foremost I am in debt to Hannes Schulz,
whose feedback proved to be invaluable during my studies.
I would like to thank Christoph Lampert for hosting me as a visiting researcher
at the IST Austria. His guidance and advice helped me in directing my further
research. My thanks are also extended to Sebastian Nowozin for his collaboration,
many helpful discussions, and advice.

I would also like to thank Carsten Rother for allowing me to work with him
at Microsoft Research Cambridge and hosting me there.

I have been lucky to be a part of the \textsc{scikit-learn} community, whose developers
have been a constant source of encouragement and inspiration to me. My
understanding of machine learning as well as software engineering has been
greatly affected by the continuing exchange with Olivier Grisel, Lars Buitinck,
Ga\"el Varoquax, Vlad Niculae, Mathieu Blondel, Gilles Louppe, Arnaud Joly and
others.

@@

the influence of caching for SZLJSP seems a promising topic for future research.

>>>>

During my work on this dissertation, my ideas were shaped by many of my fellow
students and researchers. First and foremost I am in debt to Hannes Schulz,
whose feedback proved to be invaluable during my studies.
I would like to thank Christoph Lampert for hosting me as a visiting researcher
at the IST Austria. His guidance and advice helped me in directing my further
research. My thanks are also extended to Sebastian Nowozin for his collaboration,
many helpful discussions, and advice.
%
I would also like to thank Carsten Rother for allowing me to work with him
at Microsoft Research Cambridge and hosting me there.

My research has been partially funded by the B-IT research school that I want to thank for my scholarship.

I have been lucky to be a part of the \textsc{scikit-learn} community, whose
developers have been a constant source of encouragement and inspiration to me.
My understanding of machine learning as well as software engineering has been
greatly affected by the continuing exchange with Olivier Grisel, Lars Buitinck,
Ga\"el Varoquax, Mathieu Blondel, Gilles Louppe, Arnaud Joly and others. In
particular I want to thank Vlad Niculae for his help during the formation of
this work.

@@

the influence of caching for SZLJSP~(see \Secref{dual_coordinate_descent})
seems a promising topic for future research.
